### 2023-11-15 Scripts/Manuscript/manuscript.Rmd
added the QMPCodingInfoTable.

The tests for hypotheses 4, 5, & 6 were all based on the number of QMPs per category that were determined by the research using the coding protocol. An overview of the QMP categories of the coding variables, based on @flake2020measurement, can be seen in Table INSERT TABLE 1 REF HERE

INSERT TABLE 1 HERE

@@

# print the table in apa formatting
apa_table(
  replication_ratio_table, align = c("l", "r", "r", "r")
  , caption = "Ratio of measures for which the effect was considered replicated, across many labs projects"
  , note = "$^a$replication was assessed as unclear for three of the measures, since their effect was not fully replicated. These have been treated as not replicated within this table and further analyses throughout the thesis"
  , escape = FALSE, placement= "h", midrules = 4)

@@

## Questionable Measurement Practices
The counts of the QMP ratio obtained for each QMP type (see Table XXX) are shown across the top layer of Figure XXX for both replication protocols and original articles. The overall number of counts for the QMP ratios of the QMP modification type were lower compared to the others, because only `r apa_num(table(coded_data_replications$mod_check)["True"])` out of `r apa_num(length(coded_data_replications$mod_check))` measures in replications, and only `r apa_num(table(coded_data_original_shortened$mod_check)["True"], numerals = FALSE)` measures used in original studies were modified. The bottom layer of Figure XXX shows the overlayed distributions of the total QMP ratios from the replication protocols and original studies, with dots indicating each datapoint, and the line indicating the mean for either distribution.

>>>>

The tests for hypotheses 4, 5, & 6 were all based on the number of QMPs per category that were determined by the research using the coding protocol. An overview of the QMP categories of the coding variables, based on @flake2020measurement, can be seen in Table \@ref(tab:QMPCodingInfoTable)

\renewcommand{\arraystretch}{0.5}
```{r QMPCodingInfoTable}
QMP_info_dataframe <-data.frame(Category = c("Definition", "", "", "Operationalisation", "", "", "", "Selection/Creation", "", "", "Quantification", "Modification", "", "", "", "", ""),
           'N Questions' = c("1", "", "", "5", "", "", "", "4", "", "", "4", "6", "", "", "", "", ""),
           'Example Question' = c("A psychological/sociological definition",
            "is given to the name of the measured",
            "variable within the paper.", 
            "The administration format (pen-and-",
            "paper/computer) and environment (in",
            "public/in a lab) are described (Note:",
            "both should be present for a true rating).", 
            "The source of the scale is provided",
            "(in case the scale was newly developed",
            "this should be clearly stated).", 
            "The number of items are described.", 
            "Any format changes are mentioned",
            "(paper-and-pencil <–> computer), if no",
            "changes were made to the format, and",
            "this was mentioned then code as No",
            "modification. If it is not clear, then code",
            "as False."))

# transfer the data to an APA table for printing
apa_table(
  QMP_info_dataframe, align = c("l", "r", "l")
  , caption = "Information of QMP coding variables per category."
  , note = "N Questions refers only to the questions considered quantative as specified in the text below."
  , escape = FALSE, placement= "ht", booktabs = TRUE)

```
\renewcommand{\arraystretch}{1}

@@

# print the table in apa formatting
apa_table(
  replication_ratio_table, align = c("l", "r", "r", "r")
  , caption = "Ratio of measures for which the effect was considered replicated, across many labs projects"
  , note = "$^a$replication was assessed as unclear for three of the measures, since their effect was not fully replicated. These have been treated as not replicated within this table and further analyses throughout the thesis"
  , escape = FALSE, placement = "ht", midrules = 4)

@@

The counts of the QMP ratio obtained for each QMP type (see Table XXX) are shown across the top layer of Figure XXX for both replication protocols and original articles. The overall number of counts for the QMP ratios of the QMP modification type were lower compared to the others, because only `r apa_num(table(coded_data_replications$mod_check)["True"])` out of `r apa_num(length(coded_data_replications$mod_check))` measures in replications, and only `r apa_num(table(coded_data_original_shortened$mod_check)["True"], numerals = FALSE)` measures used in original studies were modified. The bottom layer of Figure XXX shows the overlayed distributions of the total QMP ratios from the replication protocols and original studies, with dots indicating each datapoint, and the line indicating the mean for either distribution.
